A Java Wrapper For Embarrassingly Parallel Problems

### 2013-11-03 paper/paper.tex
More paper

The framework provides a "wrapper' for the original program that mimics the
behavior of the original program. It calls the serial programs on multiple Java 
threads. Each thread acts like the serial application, reading a subset of the 
input the same and creating the output in the same format. This paper describes
a framework a framework that makes it easy to parallelize an embarrassingly
parallel program that reads from a file, writes to a file and whose input can be
broken up into work units by a regular expression. The framework gives an
exponential decrease in runtime as more processor help in the computation. This
decrease levels off between 50 and 100\% CPU usage due to the other tasks on the
machine that take up memory.

@@

REDO THIS PART
The Ka/Ks Calculator is not the only embarrassingly parallel program that has the
potential to take several days to run on a data set. In fact, there are several
embarrassingly parallel programs in the biological sciences. 
TALK ABOUT CLUSTERING
With several applications that 
would benefit from parallelism in this field, it was obvious it would be 
desirable to develop a framework for creating wrapper programs.

@@

\section{Proposed Solution}

A UML Diagram will go here

The KaKs Calculator is not the only program to use the framework; there are
various potential programs that the framework could support. The only 
requirements for the this program are that it process the input in an 
embarrassingly parallel manner and that the input comes from a file and the 
processed results are also writen to a file. The framework needs to support 
various kinds of input files and be able to chunk up the work accordingly. The 
Ka/Ks Calculator's input consists of a header and then two protein sequence 
lines followed by a blank line. The framework uses that blank line to know when 
one chunk of work has ended and another has begun. The user can input a regular 
expression to define what lines of input make up what chunks. This occurs in 
the ChunkManager class.

@@

\begin{figure}
{{!}{\includegraphics{experiment/out.png}}}
\caption{Runtimes for the Ka/Ks Calculator though the framework}
\label{fig:graph}
\end{figure}

>>>>

The framework provides a "wrapper" for the original program that mimics the
behavior of the original program. It calls the serial programs on multiple Java 
threads. Each thread acts like the serial application, reading a subset of the 
input the same and creating the output in the same format. This paper describes
a framework a framework that makes it easy to parallelize an embarrassingly
parallel program that reads from a file, writes to a file and whose input can be
broken up into work units by a regular expression. The framework gives an
exponential decrease in runtime as more processor help in the computation. This
decrease levels off between 50 and 100\% CPU usage due to the other tasks on the
machine that take up memory.

@@

The Ka/Ks Calculator is not the only embarrassingly parallel program that has the
potential to take several days to run on a data set. In fact, there are several
embarrassingly parallel programs in the biological sciences. 
TALK ABOUT CLUSTERING
With several applications that 
would benefit from parallelism in this field, it was obvious it would be 
desirable to develop a framework for creating wrapper programs.

@@

\section{Proposed Solution}
\begin{figure}
{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
\caption{UML for the embarrassingly parallel framework}
\label{fig:uml}
\end{figure}
The KaKs Calculator is not the only program to use the framework; there are
various potential programs that the framework could support. The only 
requirements for the this program are that it process the input in an 
embarrassingly parallel manner and that the input comes from a file and the 
processed results are also writen to a file. The framework needs to support 
various kinds of input files and be able to chunk up the work accordingly. The 
Ka/Ks Calculator's input consists of a header and then two protein sequence 
lines followed by a blank line. The framework uses that blank line to know when 
one chunk of work has ended and another has begun. The user can input a regular 
expression to define what lines of input make up what chunks. This occurs in 
the ChunkManager class.

@@

\begin{figure}
{\resizebox{5.2in}{!}{\includegraphics{experiment/out.png}}}
\caption{Runtimes for the Ka/Ks Calculator though the framework}
\label{fig:graph}
\end{figure}
